Constraints on tensor and scalar couplings from $B\to K\bar\mu\mu$ and $B_s\to \bar\mu\mu$

### 2015-10-27 tensor/draft/draft-tensor-op.tex
[tensor] Update intervals on marginals and post. predictive for some T5 fits
[tensor-draft] corrected sign in eq.(3.2) for C_T5 -> - C_T5
[draft-tensor-op.tex] updated predictions for most general scenario

%%
%% Comments
%%
\newcommand{\christoph}[1]{{\color{red}{#1}}}
\newcommand{\fred}[1]{{\color{green}{#1}}}
\newcommand{\todo}[1]{{\color{magenta}{ {\bf ToDo: }{#1}}}}
\newcommand{\checked}[1]{{\color{brown}{ {\bf Checked: }{#1}}}}
\renewcommand{\checked}[1]{#1}

@@

There are some angular observables $J_i$ in $B\to K^*(\to K\pi)\, \bar\ell\ell$
with the same properties; i.e. tensor and scalar contributions are kinematically
enhanced by a factor $\sqrt{q^2}/m_\ell$ over vector ones present in the SM or
their respective interference terms. These are $J_{6c}$ and the two linear
combinations $(J_{1s} - 3 J_{2s})$ and $(J_{1c} + J_{2c})$ with explicit
formulas given in \refapp{app:BKstarellell}. In our fits and predictions we
include all kinematically suppressed terms. But for the purpose of illustration,
we now consider the analytical dependence for vanishing lepton mass. In this
limit,
\begin{align}
  J_{6c} & \propto
    \mbox{Re}\big[(\wilson[]{P} - \wilson[]{P'})\, \wilson[\ast]{T}
                - (\wilson[]{S} - \wilson[]{S'})\, \wilson[\ast]{T5}\big]
\intertext{is sensitive to the interference of tensor and scalar operators,
  complementary to $A_{\rm FB}^\ell$ in $B\to K \bar\ell\ell$}
  \label{eq:AFB-dependence}
  A_{\rm FB}^\ell & \propto
    \mbox{Re}\big[(\wilson[]{P} + \wilson[]{P'})\, \wilson[\ast]{T5}
                + (\wilson[]{S} + \wilson[]{S'})\, \wilson[\ast]{T}\big]
                \Big/ \Gamma_\ell \,,
\end{align}
i.e., with an interchange of tensor contributions $T \leftrightarrow T5$.  We
note also that $J_{6c}$ contributes to the lepton forward-backward asymmetry of
$B\to K^* \bar\ell\ell$ being $\propto (J_{6s} + J_{6c}/2)$. Since it has to
compete with $J_{6s}$ in this observable, a separate measurement of $J_{6s}$ and
$J_{6c}$ is necessary.

@@

\begin{table*}
  \renewcommand{\arraystretch}{1.3}
  \begin{center}
  \begin{tabular}{cccc}
  \hline
  data set
  & only $F_H^\mu$
  & $F_H^\mu$ + other
  & $F_H^\mu$ + other
  \\
  set of couplings
  & $\wilson{T,\,T5}$
  & $\wilson{T,\,T5}$
  & $\wilson{T,\,T5,\, 9,\,10}$
  \\
  credibility level
  & 68\%, 95\%
  & 68\%, 95\%
  & 68\%, 95\%
  \\
  \hline
  $\mbox{Re}\,\wilson{T}$
  & $\quad$ $[-0.32,\, 0.16]$, $[-0.52,\, 0.35]$ $\quad$
  & $\quad$ $[-0.29,\, 0.09]$, $[-0.43,\, 0.27]$ $\quad$
  & $\quad$ $[-0.23,\, 0.14]$, $[-0.39,\, 0.30]$ $\quad$
  \\
  $\mbox{Im}\,\wilson{T}$
  & $[-0.25,\, 0.24]$, $[-0.44,\, 0.44]$
  & $[-0.19,\, 0.21]$, $[-0.37,\, 0.35]$
  & $[-0.17,\, 0.22]$, $[-0.33,\, 0.37]$
  \\[0.1cm]
  $\mbox{Re}\,\wilson{T5}$
  & $[-0.25,\, 0.24]$, $[-0.44,\, 0.44]$
  & $[-0.19,\, 0.17]$, $[-0.33,\, 0.33]$
  & $[-0.18,\, 0.16]$, $[-0.32,\, 0.32]$
  \\
  $\mbox{Im}\,\wilson{T5}$
  & $[-0.24,\, 0.25]$, $[-0.44,\, 0.45]$
  & $[-0.21,\, 0.19]$, $[-0.37,\, 0.35]$
  & $[-0.20,\, 0.18]$, $[-0.36,\, 0.35]$
  \\
  \hline
  \end{tabular}

@@

The most general fit of complex-valued tensor and scalar couplings
$\wilson{S,S',P,P',T,T5}$ in combination with vector couplings
$\wilson{9,\,9',\,10,\, 10'}$---the combination of \refsec{sec:tensor}
and \refsec{sec:scalar}---yields bounds very similar to those in
tables \ref{tab:cTT5:1-dimCLs} and~\ref{tab:cSP:1-dimCLs}. The changes
are only small and in fact the bounds tend to be even more stringent
by $\sim (10 - 20) \%$ because tensor and scalar couplings can
contribute to $F_H^{\mu}$ only constructively---see
\refeq{eq:FH-dependence}.  As before, branching-ratio measurements of
$B\to K^{*}\bar\mu\mu$ help to improve the constraints on
$\wilson{T,\, T5}$. This demonstrates that even in the case of
complex-valued couplings there is enough information in the data to
bound all 20 real and imaginary parts.

@@

\begin{table*}
  \renewcommand{\arraystretch}{1.5}
  \begin{center}
  \begin{tabular}{cccccc}
  \hline
    observable
  & $q^2$-bin [GeV$^2$]
  & SM
  & $\quad T(5),\,9,\,10\quad$
  & $\quad S^{(')},\,P^{(')},\,9^{(')},\,10^{(')} \quad$
  & $\quad S^{(')},P^{(')},\,T(5),\,9^{(')},10^{(')}$
  \\
  \hline
  \multirow{2}{*}{$\tau_{B^0} \times J_{6c}$}
  & $[1.1,\, 6]$
  & $\simeq 0$
  & $(0.6_{-1.9}^{+1.8}) \cdot 10^{-9\;}$
  & $(-0.1_{-1.9}^{+2.3}) \cdot 10^{-10}$
  & $(0.2_{-1.1}^{+1.1}) \cdot 10^{-9}$
  \\
  & $[15,\, 19]$
  & $\simeq 0$
  & $(2.1_{-6.2}^{+5.1}) \cdot 10^{-10}$
  & $(0.7_{-6.6}^{+5.4}) \cdot 10^{-11}$
  & $(-0.2_{-2.9}^{+3.5}) \cdot 10^{-11}$
  \\
  \hline
  \multirow{2}{*}{$\tau_{B^0} \times (J_{1c} + J_{2c})$}
  & $[1.1,\, 6]$
  & $(3.30_{-0.56}^{+0.65}) \cdot 10^{-9\;}$
  & $(4.8_{-1.9}^{+1.7}) \cdot 10^{-9\;}$
  & $(2.6_{-0.4}^{+0.5}) \cdot 10^{-9\;}$
  & $(2.8_{-1.1}^{+1.5}) \cdot 10^{-9}$
  \\
  & $[15,\, 19]$
  & $(1.72_{-0.16}^{+0.16}) \cdot 10^{-10}$
  & $(4.7_{-2.6}^{+3.3}) \cdot 10^{-9\;}$
  & $(1.9_{-0.7}^{+0.3}) \cdot 10^{-10}$
  & $(3.1_{-2.3}^{+2.5}) \cdot 10^{-9}$
  \\
  \hline
  \multirow{2}{*}{$\tau_{B^0} \times (J_{1s} - 3 J_{2s})$}
  & $[1.1,\, 6]$
  & $(2.44_{-0.48}^{+0.46}) \cdot 10^{-10}$
  & $(1.9_{-1.1}^{+1.4}) \cdot 10^{-8\;}$
  & $(4.0_{-1.2}^{+1.6}) \cdot 10^{-10}$
  & $(1.5_{-1.1}^{+1.0}) \cdot 10^{-8}$
  \\
  & $[15,\, 19]$
  & $(1.12_{-0.10}^{+0.10}) \cdot 10^{-10}$
  & $(7.1_{-3.8}^{+5.6}) \cdot 10^{-9\;}$
  & $(1.4_{-0.4}^{+0.3}) \cdot 10^{-10}$
  & $(5.3_{-3.8}^{+3.8}) \cdot 10^{-9}$
  \\
  \hline
  $A_{\Delta \Gamma}(B_s \to \bar\mu\mu)$
  & --
  & 1
  & 1
  & $[-1,\, 1]$
  & $[-1,\, 1]$
  \\
  \hline
  \end{tabular}
  \end{center}
  \renewcommand{\arraystretch}{1.0}
  \caption{
     \label{tab:postdictions}
     The posterior predictive 68\% probability intervals of not-yet-measured
     angular observables for several new-physics scenarios given all the
     considered experimental constraints. The corresponding values for the
     SM (prior predictive) are given, too, where ``$\simeq 0$'' indicates
     zero in the considered approximation, see text for details.
   }
\end{table*}

>>>>

%%
%% Comments
%%
\newcommand{\christoph}[1]{{\color{red}{#1}}}
\newcommand{\fred}[1]{{\color{green}{#1}}}
\newcommand{\update}[1]{{\color{red}{#1}}}
\newcommand{\todo}[1]{{\color{magenta}{ {\bf ToDo: }{#1}}}}
\newcommand{\checked}[1]{{\color{brown}{ {\bf Checked: }{#1}}}}
\renewcommand{\checked}[1]{#1}

@@

There are some angular observables $J_i$ in $B\to K^*(\to K\pi)\, \bar\ell\ell$
with the same properties; i.e. tensor and scalar contributions are kinematically
enhanced by a factor $\sqrt{q^2}/m_\ell$ over vector ones present in the SM or
their respective interference terms. These are $J_{6c}$ and the two linear
combinations $(J_{1s} - 3 J_{2s})$ and $(J_{1c} + J_{2c})$ with explicit
formulas given in \refapp{app:BKstarellell}. In our fits and predictions we
include all kinematically suppressed terms. But for the purpose of illustration,
we now consider the analytical dependence for vanishing lepton mass. In this
limit,
\begin{align}
  J_{6c} & \propto
    \mbox{Re}\big[(\wilson[]{P} - \wilson[]{P'})\, \wilson[\ast]{T}
                \update{+ (\wilson[]{S} - \wilson[]{S'})\, \wilson[\ast]{T5}}\big]
\intertext{is sensitive to the interference of tensor and scalar operators,
  complementary to $A_{\rm FB}^\ell$ in $B\to K \bar\ell\ell$}
  \label{eq:AFB-dependence}
  A_{\rm FB}^\ell & \propto
    \mbox{Re}\big[(\wilson[]{P} + \wilson[]{P'})\, \wilson[\ast]{T5}
                + (\wilson[]{S} + \wilson[]{S'})\, \wilson[\ast]{T}\big]
                \Big/ \Gamma_\ell \,,
\end{align}
i.e., with an interchange of tensor contributions $T \leftrightarrow T5$.  We
note also that $J_{6c}$ contributes to the lepton forward-backward asymmetry of
$B\to K^* \bar\ell\ell$ being $\propto (J_{6s} + J_{6c}/2)$. Since it has to
compete with $J_{6s}$ in this observable, a separate measurement of $J_{6s}$ and
$J_{6c}$ is necessary.

@@

\begin{table*}
  \renewcommand{\arraystretch}{1.3}
  \begin{center}
  \begin{tabular}{cccc}
  \hline
  data set
  & only $F_H^\mu$
  & $F_H^\mu$ + other
  & $F_H^\mu$ + other
  \\
  set of couplings
  & $\wilson{T,\,T5}$
  & $\wilson{T,\,T5}$
  & $\wilson{T,\,T5,\, 9,\,10}$
  \\
  credibility level
  & 68\%, 95\%
  & 68\%, 95\%
  & 68\%, 95\%
  \\
  \hline
  $\mbox{Re}\,\wilson{T}$
  & $\quad$ $[-0.32,\, 0.16]$, $[-0.52,\, 0.35]$ $\quad$
  & $\quad$ \update{$[-0.26,\, 0.10]$, $[-0.40,\, 0.26]$} $\quad$
  & $\quad$ \update{$[-0.24,\, 0.14]$, $[-0.38,\, 0.30]$} $\quad$
  \\
  $\mbox{Im}\,\wilson{T}$
  & $[-0.25,\, 0.24]$, $[-0.44,\, 0.44]$
  & \update{$[-0.18,\, 0.20]$, $[-0.34,\, 0.36]$}
  & \update{$[-0.16,\, 0.22]$, $[-0.34,\, 0.36]$}
  \\[0.1cm]
  $\mbox{Re}\,\wilson{T5}$
  & $[-0.25,\, 0.24]$, $[-0.44,\, 0.44]$
  & \update{$[-0.24,\, 0.08]$, $[-0.38,\, 0.24]$}
  & \update{$[-0.24,\, 0.10]$, $[-0.38,\, 0.26]$}
  \\
  $\mbox{Im}\,\wilson{T5}$
  & $[-0.24,\, 0.25]$, $[-0.44,\, 0.45]$
  & \update{$[-0.20,\, 0.18]$, $[-0.36,\, 0.34]$}
  & \update{$[-0.18,\, 0.20]$, $[-0.34,\, 0.36]$}
  \\
  \hline
  \end{tabular}

@@

The most general fit of complex-valued tensor and scalar couplings
$\wilson{S,S',P,P',T,T5}$ in combination with vector couplings
$\wilson{9,\,9',\,10,\, 10'}$---the combination of \refsec{sec:tensor}
and \refsec{sec:scalar}---yields bounds very similar to those in
tables \ref{tab:cTT5:1-dimCLs} and~\ref{tab:cSP:1-dimCLs}. The changes
are only small and in fact the bounds tend to be even more stringent
\update{by $\sim (10 - 30) \%$} because tensor and scalar couplings can
contribute to $F_H^{\mu}$ only constructively---see
\refeq{eq:FH-dependence}.  As before, branching-ratio measurements of
$B\to K^{*}\bar\mu\mu$ help to improve the constraints on
$\wilson{T,\, T5}$. This demonstrates that even in the case of
complex-valued couplings there is enough information in the data to
bound all 20 real and imaginary parts.

@@

\begin{table*}
  \renewcommand{\arraystretch}{1.5}
  \begin{center}
  \begin{tabular}{cccccc}
  \hline
    observable
  & $q^2$-bin [GeV$^2$]
  & SM
  & $\quad T(5),\,9,\,10\quad$
  & $\quad S^{(')},\,P^{(')},\,9^{(')},\,10^{(')} \quad$
  & $\quad S^{(')},P^{(')},\,T(5),\,9^{(')},10^{(')}$
  \\
  \hline
  \multirow{2}{*}{$\tau_{B^0} \times J_{6c}$}
  & $[1.1,\, 6]$
  & $\simeq 0$
  & \update{$(0.6_{-1.9}^{+1.7}) \cdot 10^{-9\;}$}
  & $(-0.1_{-1.9}^{+2.3}) \cdot 10^{-10}$
  & \update{$(0.0_{-0.9}^{+1.1}) \cdot 10^{-9}$}
  \\
  & $[15,\, 19]$
  & $\simeq 0$
  & \update{$(1.7_{-5.6}^{+5.3}) \cdot 10^{-10}$}
  & $(0.7_{-6.6}^{+5.4}) \cdot 10^{-11}$
  & \update{$(-0.1_{-3.0}^{+3.5}) \cdot 10^{-10}$}
  \\
  \hline
  \multirow{2}{*}{$\tau_{B^0} \times (J_{1c} + J_{2c})$}
  & $[1.1,\, 6]$
  & $(3.30_{-0.56}^{+0.65}) \cdot 10^{-9\;}$
  & \update{$(3.6_{-1.1}^{+2.1}) \cdot 10^{-9\;}$}
  & $(2.6_{-0.4}^{+0.5}) \cdot 10^{-9\;}$
  & \update{$(3.3_{-1.2}^{+2.5}) \cdot 10^{-9}$}
  \\
  & $[15,\, 19]$
  & $(1.72_{-0.16}^{+0.16}) \cdot 10^{-10}$
  & \update{$(4.3_{-2.5}^{+3.1}) \cdot 10^{-9\;}$}
  & $(1.9_{-0.7}^{+0.3}) \cdot 10^{-10}$
  & \update{$(2.8_{-2.2}^{+3.0}) \cdot 10^{-9}$}
  \\
  \hline
  \multirow{2}{*}{$\tau_{B^0} \times (J_{1s} - 3 J_{2s})$}
  & $[1.1,\, 6]$
  & $(2.44_{-0.48}^{+0.46}) \cdot 10^{-10}$
  &  \update{$(2.0_{-1.3}^{+1.3}) \cdot 10^{-8\;}$}
  & $(4.0_{-1.2}^{+1.6}) \cdot 10^{-10}$
  & \update{$(1.0_{-0.7}^{+1.2}) \cdot 10^{-8}$}
  \\
  & $[15,\, 19]$
  & $(1.12_{-0.10}^{+0.10}) \cdot 10^{-10}$
  &  \update{$(7.8_{-4.9}^{+4.2}) \cdot 10^{-9\;}$}
  & $(1.4_{-0.4}^{+0.3}) \cdot 10^{-10}$
  & \update{$(4.6_{-3.6}^{+4.3}) \cdot 10^{-9}$}
  \\
  \hline
  $A_{\Delta \Gamma}(B_s \to \bar\mu\mu)$
  & --
  & 1
  & 1
  & $[-1,\, 1]$
  & $[-1,\, 1]$
  \\
  \hline
  \end{tabular}
  \end{center}
  \renewcommand{\arraystretch}{1.0}
  \caption{
     \label{tab:postdictions}
     The posterior predictive 68\% probability intervals of not-yet-measured
     angular observables for several new-physics scenarios given all the
     considered experimental constraints. The corresponding values for the
     SM (prior predictive) are given, too, where ``$\simeq 0$'' indicates
     zero in the considered approximation, see text for details.
   }
\end{table*}
